Irt plot extra

### 2023-11-05 manuscript.Rmd
Revision 1 (MASJ)

@@

>>>>

desctable.data %>%
  tbl_summary(
    by=slypos_demographics_sex.factor,
    statistic=list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    digits=all_continuous() ~ 2,
    label=list(slypos_demographics_age ~ "Age",
                 # slypos_demographics_sex.factor ~ "Sex",
                 slypos_demographics_gender.factor ~ "Gender-Variant Identity",
                 slypos_demographics_language.factor ~ "Native English Speaker",
                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
                 slypos_demographics_school.factor ~ "Occupational setting"
                 ),

    missing="no"
    ) %>% add_overall() %>% bold_labels() %>% 
  # add_p() %>% add_q() %>%
modify_header(label ~ "**Variable**") %>% 
  # separate_p_footnotes() %>%
  modify_caption("Demographic Characteristics of Participants (n=690).") -> desc_table_gender

@@

# # create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
# desctable.data %>%
#   tbl_summary(
#     by=slypos_demographics_sex.factor,
#     statistic=list(all_continuous() ~ "{mean} ({sd})",
#                      all_categorical() ~ "{n} ({p}%)"),
#     digits=all_continuous() ~ 2,
#     label=list(slypos_demographics_age ~ "Age",
#                  # slypos_demographics_sex.factor ~ "Sex",
#                  slypos_demographics_gender.factor ~ "Gender-Variant Identity",
#                  slypos_demographics_language.factor ~ "Native English Speaker",
#                  slypos_demographics_work_or_school.factor ~ "Occupational Status",
#                  slypos_demographics_school.factor ~ "Occupational setting"
#                  ),
#     
#     missing="no"
#     ) %>% add_overall() %>% bold_labels() %>% 
#   # add_p() %>% add_q() %>%
# modify_header(label ~ "**Variable**") %>% 
#   # separate_p_footnotes() %>%
#   modify_caption("Demographic Characteristics of Participants (n=690).") -> desc_table 
# 
# as_tibble(desc_table) -> desc_tibble 
# as_kable_extra(desc_table, format="latex",booktabs=T) -> desc_kable #save it as a knitr::kable
